Robust Energy-Aware Routing with Uncertain Traffic Demands

### 2014-11-20 paper.tex
Add 85 & 95 real result

>>>>

\section{Algorithm}
In our paper, Robust Energy-Aware Routing (REAR) algorithm works in two phases. Firstly, REAR select links 
should be sleeping from the origin topology based on extended algebraic connectivity, then compute the robust 
routing by demand-oblivious routing algorithm.

\subsection{First Phase}

\subsubsection{Extend Algebraic Connectivity}
Network topology is represented by $G = (V, E)$ as mentioned in Model section, where $V$ is the set of vertices
and $E$ is the set of links. We say $A(G)$ is the Adjacency Matrix of graph $G$, that include information for which
vertices of the graph are adjacent to which other vertices. $A(G)$ is a $N \times N$ matrix, where
$N = |V|$ and non-diagonal entry $a_{ij}$ equal to the number of edges from vertex $i$ to vertex $j$, in this paper,
$a_{ij}$ always be 1 if $(i,j) \in E$ otherwise 0. And we stipulate the diagonal element $a_{ii}$ be 0.

We say $D(G)$ is the Degree Matrix of graph $G$, which is a diagonal matrix and diagonal entry $d_{ii}$ denote 
the degree of node $i$. It is obvious that there is $d_{ii} == \sum_{j} a_{ij}$.

Then we define Laplacian Matrix $L(G)$ of graph $G$ as the difference between Degree Matrix and Adjacency Matrix :
\begin{equation}
	L(G) = D(G) - A(G)
\end{equation}
where $D(G)$ is the Degree Matrix and $A(G)$ is the Adjacency Matrix.

In the mathematical field of graph theory, the algebraic connectivity of a graph $G$ is the second-smallest
eigenvalue of the Laplacian Matrix. This eigenvalue is greater than 0 if and only if $G$ is connected, and 
it measures the connectivity of graph, the greater of which, the more connective of graph.

As far as we know, 
algebraic connectivity regard every link the same, without considering the capacity of each one, but it is 
ridiculous in network. It is easy to see, link with greater capacity is more important than the same one
with lower capacity. So we extend the algebraic connectivity definition by following ways:

\begin{enumerate}
	\item We change the Adjacency Matrix from binary-matrix to float-matrix, i.e. if $(i,j) \in E$ we set the $a_{ij}$
with the capacity of link $l_{ij}$ instead of binary value 1.
	\item Degree Matrix is not ever the denotation for the degree of nodes, but the conbined capacity of all the links
adjacent to the node, there is still exist the equation: $d_{ij} == \sum_{j} a_{ij}$
	\item No modification for definition of Laplacian Matrix
\end{enumerate}

We calculate new extend algebraic connectivity from the new Laplacian matrix, denoted by $\lambda_2(G)$.

Topology always have different extend algebraic connectivity values, it is clear that when one link is added or 
removed from the graph, the extend algebraic connectivity value changes accordingly. And we say the changed value
is the impact of this link on the graph. Supposed we sleep link $l$ from graph $G$, new graph is described as $G^*$, 
we defined the impact of link $l$ as :
\begin{equation}
	\Delta_l = \lambda_2(G) - \lambda_2(G^*)
\end{equation}
where $\lambda_2(G)$ and $\lambda_2(G^*)$ is extend algebraic connectivity of $G$ and $G^*$ respectly.

Clearly, $\Delta_l$ is always greater than 0, because graph will always lose connectivity when link is removed.
Further more, some link will play a more important role in the connectivity of graph, such as the backbone link 
of network topology. And we say a link $l$ affect more if $\Delta_l$ is greater.

\subsection{First Phase Description}
REAR sleep as many links as possible without losing much connectivity of graph. Originly,  we should
calculate impact of all the links and sleep the lowest one from the graph, then repeat calculate and remove
process until arrive some specific threhold. Obviously, it is NP-Hard, following is a heuristic algorithm.

For the origin graph, we calculate the impact of every link as $\Delta_{l_i}$ , and then sort these values
from small to big, output ordered list denoted as $\Gamma$: 
\begin{equation}
	\Gamma = {..., l_i, ..., l_j, ...}
\end{equation}
where $\Delta_{l_i} < \Delta_{l_j}$.

Pay attention we only compute the link impact once at the begining of algorihtm, and the ordered list $\Gamma$ show 
the order of `importantance` among links in the connectivity of the graph.

Now we begin selecting which links should be sleep.
We denote the set of the sleeping links as $S$, and the output of this phase is final graph $G^* = (V, E-S)$. We set 
$S = \emptyset$, and repeat our selecting process, each iteration we select one link and put it into $S$. 
In iteration $i$, algorithm scan links as the order of $\Gamma$ and choose one which is still not in the $S$, we try to
remove this link from the graph, if some metric of the current graph do not arrive the threhold we put the link into
$S$ then go next iteration, or choose the next link from the $\Gamma$ for trying to remove otherwise. Algorithm
stop until all the links in $\Gamma$ is tried but there is no one to satisfy the threhold.

So before going ahead our algorithm, there is another thing we should done, what is the threhold for the graph.
It does matter for what we concern most of the graph, in our graph, we choose two threholds, one is connectivity and
another is power consumption. For considering connectivity , we defined the difference of connectivity between 
two graphs as:
\begin{equation}
	diff_c = \lambda_2(G_{S, l}^o) / \lambda_2(G^o) * 100
\end{equation}
where $\lambda_2(G_{S, l}^o)$ is the extend algebraic connectivity of the final graph, when the links set $S$ and 
link $l$ are both removed from the origin graph $G^o$, and the $\lambda_2(G^o)$ is the extend algebraic connectivity of 
the origin graph.

If we set $diff_c$ valued 90\%, it means that whenever we try to remove the link $l$ from the origin graph in 
iteration, the extend algebraic connectivity should never lower than the 90\% of origin one. For power consumption
consideration, we simply take an power model from `Green TE` showed in Table xx, and defined the difference of 
power consumption between two graphs as:
\begin{equation}
	diff_p = \rho(G_{S, l}^o) / \rho(G^o) * 100
\end{equation}
where $\rho(G^o)$ is the power consumption of the origin graph, and $\rho(G_{S, l}^o)$ is similar with the 
definition above.

Experiment shows that...

\subsection{Second Phase}
When we get the output graph from the first phase based on extend algebraic connectivity, it is time to compute
the robust routing.
